---
title: "model_details"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{model_details}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r global_options}
knitr::opts_chunk$set(eval = FALSE)
```

# Overview

This package summarizes and displays the number of US highway traffic accidents on the map using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System.

The name of data files to read is "accident_(year).csv.bz2" and the (year) is numeric year such as 2013.

# Functions

## fars_summarize_years
fars_summarize_years function shows the number of accidents in each month during the given year or years. The function takes year as numeric argument.

```{r}
fars_summarize_years(2013)
```

```{r}
fars_summarize_years(2013:2015)
```

## fars_map_state
fars_map_state function displays the accidents of a state in a given year as a map. First argument is the state code (from 01 to 50) and the second argument is the year.
```{r}
fars_map_state(01, 2015)
```
